
% \nocite{*}
% \addcontentsline{toc}{section}{Publications}
% \printbibliography[title=Publications]

% Can instead manually enter publications as shown:
\section{Publications}

Full list of publications on \href{https://scholar.google.com/citations?user=dwP6HwsAAAAJ&hl=en}{Google scholar}

\orderedouterlist{
\entry{
  {\bf N. Antonello}, P. N. Garner, ``A t-distribution based operator for enhancing out of distribution robustness of neural network classifiers,'' {\em IEEE Signal Process. Letters}, vol. 27, pp.1070-1074, 2020.
  }

\entry{
  {\bf N. Antonello}, E. De Sena, M. Moonen, P. A. Naylor, and T. van Waterschoot, ``Joint acoustic localization and dereverberation through plane wave decomposition and sparse regularization,'' {\em IEEE/ACM Trans. Audio, Speech Lang. Process.}, vol. 27, no. 12, pp. 1893-1905, Dec. 2019.
  }

\entry{

  {\bf N. Antonello}, E. De Sena, M. Moonen, P. A. Naylor and T. van Waterschoot, ``Room impulse
response interpolation using a sparse spatio-temporal representation of a reverberant sound
field'', {\em IEEE/ACM Trans. Audio, Speech Lang. Process.}, vol. 25, no. 10, pp. 1929-1941, Oct. 2017.

}

\entry{
E. De Sena, {\bf N. Antonello}, M. Moonen, and T. van Waterschoot, ``On the modeling of rectangular geometries in room acoustic simulations'', {\em IEEE/ACM Trans. Audio, Speech Lang. Process.}, vol. 23, no.6, pp. 774-768, Apr. 2015.\\[3pt]
}

}


\section{Patents}
\orderedouterlist{

\entry{
{    A. Salarian,
    M. Cernak,
    P. Mainar,
    J. Chardon
    {\bf N. Antonello},``Hybrid voice command processing,'' US11763814B2, Dec. 2022.
}

\entry{
{F. T. Agerkvist, {\bf N. Antonello}, and A. Christensen},``Loudspeaker assembly with suppression of magnetic flux modulation distortion,'' WO Patent App. PCT/EP2014/073 655, May 2015.
}
}
}
